Paper analysis

### 2025-04-04 Paper_analysis.Rmd
another update
another update to site

```{r shap_nexp, fig.width=9}

cowplot::plot_grid(
  sv_importance(ex.nexpbase.glb) + egg::theme_article(), 
  sv_importance(ex.nexpmarg.glb) + egg::theme_article(),
  ncol = 2
)

@@

```{r shap_qb_margshap, fig.width=9}
cowplot::plot_grid(
  sv_dependence(ex.qbmarg.glb, v="ann_agr_cohesion") + egg::theme_article(),
  sv_dependence(ex.qbmarg.glb, v="prn_pagr") + egg::theme_article(),
  sv_dependence(ex.qbmarg.glb, v="prn_agr_para_mn") + egg::theme_article(),
  ncol=2, align = "v"
)

@@

qbmarg.ann_agr_cohesion.pdp = FeatureEffect$new(pred.qb_margin, 
                                             feature = "ann_agr_cohesion",
                                             method = "pdp")
qbmarg.prn_pagr.pdp = FeatureEffect$new(pred.qb_margin, 
                                             feature = "prn_pagr",
                                             method = "pdp")
qbmarg.prn_agr_para_mn.pdp = FeatureEffect$new(pred.qb_margin, 
                                             feature = "prn_agr_para_mn",
                                             method = "pdp")

qbmarg.ann_agr_cohesion.ale = FeatureEffect$new(pred.qb_margin, 
                                              feature = "ann_agr_cohesion",
                                              method = "ale")
qbmarg.prn_pagr.ale = FeatureEffect$new(pred.qb_margin, 
                                              feature = "prn_pagr",
                                              method = "ale")
qbmarg.prn_agr_para_mn.ale = FeatureEffect$new(pred.qb_margin, 
                                              feature = "prn_agr_para_mn",
                                              method = "ale")

@@

  qbmarg.prn_agr_para_mn.pdp$plot() + ggtitle("prn_agr_para_mn PDP") + ylab("PDP") +
    egg::theme_article(),
  qbmarg.prn_agr_para_mn.ale$plot() + ggtitle("prn_agr_para_mn ALE") + ylab("ALE") +
    egg::theme_article(),

@@

```{r paircor}
selectedvar <- c("ntr_pland", "ann_agr_pland", "ntr_ed", 
                 "field_frac_mn", "prn_pagr", "prn_agr_para_mn",
                 "ann_agr_ed", "ann_agr_cohesion"
                 )

@@

```{r force_fcns}
source("R/utils-shap.r")
focus.vars <- function(x.features){
  dplyr::case_match(
    x.features,
    "ntr_pland" ~ "Natural land cover",
    "ann_agr_pland" ~ "Annual ag. land cover",
    "field_frac_mn" ~ "Field fractal dimension",
    "prn_pagr" ~ "Agriculture % perennial",
    "prn_agr_para_mn" ~ "Perennial ag. perimeter:area",
    "ann_agr_ed" ~ "Annual ag. edge density",
    "ann_agr_cohesion" ~ "Annual ag. cohesion",
    .default = "Other features"
  )
}

feature.colors <- c(
  "Natural land cover" = "#33a02c",
  "Annual ag. land cover" = "#fdbf6f",
  "Field fractal dimension" = "#56B4E9",
  "Agriculture % perennial" = "#CC79A7",
  "Perennial ag. perimeter:area" = "#D55E00",
  "Annual ag. edge density" = "#F0E442",
  "Annual ag. cohesion" = "#0072B2",
  "Other features" = "gray80"
)

>>>>

```{r shap_nexp2, fig.width=9}

cowplot::plot_grid(
  sv_importance(ex.nexpbase.glb) + egg::theme_article(), 
  sv_importance(ex.nexpmarg.glb) + egg::theme_article(),
  ncol = 2, align = "v"
)

@@

```{r shap_qb_margshap, fig.width=9}
cowplot::plot_grid(
  sv_dependence(ex.qbmarg.glb, v="ann_agr_cohesion") + egg::theme_article(),
  sv_dependence(ex.qbmarg.glb, v="prn_pagr") + egg::theme_article(),
  ncol=2, align = "v"
)

@@

qbmarg.ann_agr_cohesion.pdp = FeatureEffect$new(pred.qb_margin, 
                                             feature = "ann_agr_cohesion",
                                             method = "pdp")
qbmarg.prn_pagr.pdp = FeatureEffect$new(pred.qb_margin, 
                                             feature = "prn_pagr",
                                             method = "pdp")

qbmarg.ann_agr_cohesion.ale = FeatureEffect$new(pred.qb_margin, 
                                              feature = "ann_agr_cohesion",
                                              method = "ale")
qbmarg.prn_pagr.ale = FeatureEffect$new(pred.qb_margin, 
                                              feature = "prn_pagr",
                                              method = "ale")

@@

    egg::theme_article(),

@@

```{r paircor}
selectedvar <- c("ntr_pland", "ann_agr_pland", "ntr_ed", 
                 "field_frac_mn", "prn_pagr",
                 "ann_agr_ed", "ann_agr_cohesion"
                 )

@@

```{r force_fcns}
source("R/utils-shap.r")
focus.vars <- function(x.features){
  dplyr::case_match(
    x.features,
    "ntr_pland" ~ "Natural land cover",
    "ann_agr_pland" ~ "Annual ag. land cover",
    "field_frac_mn" ~ "Field fractal dimension",
    "prn_pagr" ~ "Agriculture % perennial",
    "ann_agr_ed" ~ "Annual ag. edge density",
    "ann_agr_cohesion" ~ "Annual ag. cohesion",
    .default = "Other features"
  )
}

feature.colors <- c(
  "Natural land cover" = "#33a02c",
  "Annual ag. land cover" = "#fdbf6f",
  "Field fractal dimension" = "#56B4E9",
  "Agriculture % perennial" = "#CC79A7",
  "Annual ag. edge density" = "#F0E442",
  "Annual ag. cohesion" = "#0072B2",
  "Other features" = "gray80"
)
